Fast and optimal centroiding of faint stars

### 2015-01-30 ms/figure.tex
Update figure.tex

Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
from the CRLB.

We found that the estimates found by 3$\times$3 polynomial method are far away from
saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation,
are much closer to the CRLB. The performance of these two methods however, is limited by
two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.

These two techniques only take advantage of the information contained in a 3$\times$3
patch around the brighest pixel of the smoothed image. Thus, when we apply 
these methods to find the centroid of stars with larger FWHM, a certain amount of
information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
of these methods deviates from the CRLB. This deviation gets even larger at lower
signal-to-noise ratios. Besides, the performance of these methods slightly degrades
in the case of undersampled stars. Presence of noise is another limitting factor.
Although these methods are able to get close to saturating the CRLB in a wide range of
signal-to-noise ratios, they are not as reliable in the extremely faint stars
(SNR less than 10). This is mostly due to the fact that presence of noise could
move the true brightest pixel of image.

In this investigation we showed that PSF fitting is always better at centroiding stars.
In practice however, we do no know the the exact PSF. Besides finding the centroid by PSF
fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial
technique into large scale astronomical surveys can considerably reduce the computational cost
of initial astrometry of these surveys. The advantage of this method becomes more pronounced
in PSF estimation in which we need to know the centroid of stars accurately, but at the
same time, with fewer number of algebraic operations. This method can roughly be thousand
times faster than centroiding by model fitting, and requires fewer operations than the
3$\times$3 quartic approximation mehod.

>>>>

Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns 
centroid estimates that saturate the CRLB; with the exception of SNR being less than 10, 
in which a few centroiding ouliers caused the RMSE to slightly, but not significantly, deviate
from the CRLB. We found that the estimates found by 3$\times$3 polynomial method are far away from
saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed
3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation,
are much closer to the CRLB. The performance of these two methods however, is limited by
two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.

These two techniques only take advantage of the information contained in a 3$\times$3
patch around the brighest pixel of the smoothed image. Thus, when we apply 
these methods to find the centroid of stars with larger FWHM, a certain amount of
information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE
of these methods deviates from the CRLB. This deviation gets even larger at lower
signal-to-noise ratios. Besides, the performance of these methods slightly degrades
in the case of undersampled stars. Presence of noise is another limitting factor.
Although these methods are able to get close to saturating the CRLB in a wide range of
signal-to-noise ratios, they are not as reliable in the extremely faint stars
(SNR less than 10). This is mostly due to the fact that in the presence of noise, 
the brightest pixel of image, does not necessarily contain the centroid of stars.

In this investigation we showed that PSF fitting is always better at centroiding stars.
In practice however, we do no know the the exact PSF. Besides finding the centroid by PSF
fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial
technique into large scale astronomical surveys can considerably reduce the computational cost
of initial astrometry of these surveys.

It is important to note that the PSF fitting method can be made faster by only keeping the 
term proportional to the product of the PSF model and the image in $\chi^2$. This is because 
the other terms are not sensitive to the position of centroid. However, this only allows
us to vary the poition of centroid, and not the flux, while fitting the PSF model
to the star.

Modifying the $\chi^2$ such that it contains the product of the PSF and image, 
provides a nice interpretation for the PSF fitting method. It corresponds to oversampling
of the image with the correct PSF, and finding the centroid in the oversampled image afterwards.
On the other hand, one can think of the initial smoothing step in 3$\times$3 methods
such as modified polynomial and quartic approximation methods, as oversampling of the 
image with an approximate Gaussian PSF. The fitting and approximate methods are different 
in that after upsamlping, in the approximate methods, our knowledge is limited to the 3$\times$3 
patch around the brightest pixel and as a result, we loose some information.

The advantage of this method becomes more pronounced
in PSF estimation in which we need to know the centroid of stars accurately, but at the
same time, with fewer number of algebraic operations. This method can roughly be thousand
times faster than centroiding by model fitting, and requires fewer operations than the
3$\times$3 quartic approximation mehod.
